Augraphy: A Data Augmentation Library for Document Images

### 2023-04-30 paper.tex
Fixed a few latex errors

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{listings}
\usepackage{times}
\renewcommand{\floatpagefraction}{.8}
\usepackage{etoolbox}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{sectsty}
\usepackage{wrapfig}
\AtBeginEnvironment{quote}{\par\singlespacing\small}

@@

@@

\begin{table}[]
    \centering
    \caption{Comparison of various image-based data augmentation libraries. Number of augmentations is a rough count, and many augmentations in other tools are what \emph{Augraphy} calls Utilities. Further, many single augmentations in \emph{Augraphy} --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
    \resizebox{0.9\textwidth}{!}{
    \begin{tabular}{lccccc}
    \toprule
         & \textbf{Number of} & \textbf{Document} & \textbf{Pipeline} & & \\
        \textbf{Library} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License} \\
    \midrule
        \emph{Augmentor} \cite{augmentor} & 27 & \xmark & \cmark & \cmark & MIT \\
        \emph{Albumentations} \cite{ref_albumentations} & 216 & \xmark & \cmark & \cmark & MIT \\
        \emph{imgaug} \cite{ref_imgaug} & 168 & \xmark & \cmark & \cmark & MIT \\
        \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & \cmark & \cmark & MIT \\
        \emph{DocCreator} \cite{ref_DocCreator} & 12 & \cmark & \xmark & \xmark & LGPL-3.0 \\
        \textbf{\emph{Augraphy} (ours)} & \textbf{\numAugraphyAugmentations} & \cmark & \cmark & \cmark & \textbf{MIT}\\
    \bottomrule
    \end{tabular}}
    \label{tab:augmentation-library-comparison}
\end{table}

@@

\begin{figure}
\centering
\scalebox{0.3}{
\includegraphics[]{figures/pipeline.png}}
\caption{Visualization of an \emph{Augraphy} pipeline, showing the composition of several image augmentations together with a specific paper background}
\label{fig:pipeline}
\end{figure}

@@

\begin{table}[]
    \centering
    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase, in suggested position within a pipeline. Augmentations that work well in more than one phase are listed in the last column.}
    \resizebox{0.9\textwidth}{!}{
    \begin{tabular}{llll}
    \toprule
        \textbf{Ink Phase} & \textbf{Paper Phase} & \textbf{Post Phase} & \textbf{Multiple} \\
        \midrule
        \textsf{BleedThrough} & \textsf{ColorPaper}& \textsf{BadPhotoCopy} & \textsf{BrightnessTexturize} \\
        \textsf{LowInkPeriodicLines} & \textsf{Watermark} & \textsf{BindingsAndFasteners} & \textsf{DirtyDrum} \\
        \textsf{LowInkRandomLines} & \textsf{Gamma} & \textsf{BookBinding} & \textsf{DirtyRollers} \\
        \textsf{InkBleed} & \textsf{LightingGradient} & \textsf{Folding} & \textsf{Dithering} \\
        \textsf{Letterpress} & \textsf{SubtleNoise} & \textsf{JPEG} & \textsf{Geometric}\\
        & \textsf{DelaunayTessellation} & \textsf{Markup} & \textsf{NoiseTexturize}\\
        & \textsf{VoronoiTesselation} & \textsf{Faxify} & \textsf{Scribbles}\\
        & \textsf{PatternGenerator}& \textsf{PageBorder} & \textsf{LinesDegradation}\\
        & & & \textsf{Brightness}\\
        \bottomrule
    \end{tabular}}
    \label{tab:augmentations}
\end{table}

@@

Consider the following sequence:
\begin{quote}
  \begin{enumerate}
  \item Ink is adhered to paper material during the initial printing of a document.
  \item The document is attached to a public bulletin board in a high-traffic area.
  \item The pages are annotated, defaced, and eventually torn away from their securing staples, flying away in the wind.
  \item Fifty years later, the tattered pages are discovered and turned over to library archivists.
  \item These conservationists use delicate tools to carefully position and record images of the document, storing these in a digital repository.
  \end{enumerate}
\end{quote}
An \texttt{AugmentationPipeline} represents such document lifetimes by composing augmentations modeling each of these individual events, while collecting runtime metadata about augmentations and their parameters and storing copies of intermediate images, allowing for inspection and fine-tuning to achieve outputs with desired features, facilitating (re)production of documents as in Figure \ref{fig:intro}.

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{courier}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{listings}
\usepackage{times}
\renewcommand{\floatpagefraction}{.8}
\usepackage{etoolbox}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{sectsty}
\usepackage{wrapfig}
\AtBeginEnvironment{quote}{\par\singlespacing\small}

@@

\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}

@@

\begin{table}
    \centering
    \caption{Comparison of various image-based data augmentation libraries. Number of augmentations is a rough count, and many augmentations in other tools are what \emph{Augraphy} calls Utilities. Further, many single augmentations in \emph{Augraphy} --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
    \resizebox{0.9\textwidth}{!}{
    \begin{tabular}{lccccc}
    \toprule
         & \textbf{Number of} & \textbf{Document} & \textbf{Pipeline} & & \\
        \textbf{Library} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License} \\
    \midrule
        \emph{Augmentor} \cite{augmentor} & 27 & \xmark & \cmark & \cmark & MIT \\
        \emph{Albumentations} \cite{ref_albumentations} & 216 & \xmark & \cmark & \cmark & MIT \\
        \emph{imgaug} \cite{ref_imgaug} & 168 & \xmark & \cmark & \cmark & MIT \\
        \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & \cmark & \cmark & MIT \\
        \emph{DocCreator} \cite{ref_DocCreator} & 12 & \cmark & \xmark & \xmark & LGPL-3.0 \\
        \textbf{\emph{Augraphy} (ours)} & \textbf{\numAugraphyAugmentations} & \cmark & \cmark & \cmark & \textbf{MIT}\\
    \bottomrule
    \end{tabular}}
    \label{tab:augmentation-library-comparison}
\end{table}

@@

\begin{figure}
\centering
\scalebox{0.3}{
\includegraphics{figures/pipeline.png}}
\caption{Visualization of an \emph{Augraphy} pipeline, showing the composition of several image augmentations together with a specific paper background}
\label{fig:pipeline}
\end{figure}

@@

\begin{table}
    \centering
    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase, in suggested position within a pipeline. Augmentations that work well in more than one phase are listed in the last column.}
    \resizebox{0.9\textwidth}{!}{
    \begin{tabular}{llll}
    \toprule
        \textbf{Ink Phase} & \textbf{Paper Phase} & \textbf{Post Phase} & \textbf{Multiple} \\
        \midrule
        \textsf{BleedThrough} & \textsf{ColorPaper}& \textsf{BadPhotoCopy} & \textsf{BrightnessTexturize} \\
        \textsf{LowInkPeriodicLines} & \textsf{Watermark} & \textsf{BindingsAndFasteners} & \textsf{DirtyDrum} \\
        \textsf{LowInkRandomLines} & \textsf{Gamma} & \textsf{BookBinding} & \textsf{DirtyRollers} \\
        \textsf{InkBleed} & \textsf{LightingGradient} & \textsf{Folding} & \textsf{Dithering} \\
        \textsf{Letterpress} & \textsf{SubtleNoise} & \textsf{JPEG} & \textsf{Geometric}\\
        & \textsf{DelaunayTessellation} & \textsf{Markup} & \textsf{NoiseTexturize}\\
        & \textsf{VoronoiTesselation} & \textsf{Faxify} & \textsf{Scribbles}\\
        & \textsf{PatternGenerator}& \textsf{PageBorder} & \textsf{LinesDegradation}\\
        & & & \textsf{Brightness}\\
        \bottomrule
    \end{tabular}}
    \label{tab:augmentations}
\end{table}

@@

\smallskip
\noindent~Consider the following sequence:
\begin{enumerate}[leftmargin=4em]
  \item Ink is adhered to paper material during the initial printing of a document.
  \item The document is attached to a public bulletin board in a high-traffic area.
  \item The pages are annotated, defaced, and eventually torn away from their securing staples, flying away in the wind.
  \item Fifty years later, the tattered pages are discovered and turned over to library archivists.
  \item These conservationists use delicate tools to carefully position and record images of the document, storing these in a digital repository.
\end{enumerate}

An \texttt{AugmentationPipeline} represents such document lifetimes by composing augmentations modeling each of these individual events, while collecting runtime metadata about augmentations and their parameters and storing copies of intermediate images, allowing for inspection and fine-tuning to achieve outputs with desired features, facilitating (re)production of documents as in Figure \ref{fig:intro}.
